### 2016-10-12 secondPaper/tex/introduction.tex

To better understand the potential for attainable shifts in
transportation behavior across the US, we employed a comparative risk
assessment methodology to compare national averages for time spent
walking and cycling for transport to those of specific states. Our
estimates can provide an important evidence base to encourage new
construction, retrofits, land use policy, and programatic funding to
support active transportation. Particularly in places with poor
attainmnet of the physical activity guidelines, such investments can
be importnat pieces of lareger population health interventions that
have effective and long-lasting impacts.

>>>>

To better understand the potential for attainable shifts in
transportation behavior across the US, we employed a comparative risk
assessment methodology to compare national averages for time spent
walking and cycling for transport to those of specific states. Our
estimates can provide an important evidence base to encourage new
construction, retrofits, land use policy, and programatic funding to
support active transportation. Particularly in places with poor
attainmnet of the physical activity guidelines, such investments can
be important pieces of larger population health interventions that
have effective and long-lasting impacts.
